---
title: "style update stats"
output:
  md_document:
    variant: markdown_github
  html_document:
    toc: true
    theme: united
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(plyr)
library(ggplot2)
```

```{r}
data <- jsonlite::fromJSON(file("style.json"))
runs <- data$values[data$values$name == 'style_update_stats', ]
style <- runs$value
style$run <- runs$run_id
style$overhead = NULL
style <- style[style$resolverAccessCount > 0, ]
style <- as.data.frame(style)
style$childTime = rowSums(style$children[colnames(style$children)], na.rm=TRUE)
```

Based on `r nrow(style)` `Document::updateStyle` observations over `r length(unique(style$run))` runs. 

Style update
------------
```{r}
ggplot(style, aes(`Document::updateStyle`)) +
  geom_line(stat="density") + scale_x_log10()

tmp <- reshape2::melt(data.frame(list(pseudo=style$counters$pseudoElementsStyled, element=style$counters$elementsStyled)))
colnames(tmp) <- c('kind', 'resolverAccessCount')

ggplot(tmp, aes(resolverAccessCount)) +
  geom_density(aes(y=..count.., fill=kind), alpha = 0.5, position="stack") + scale_x_log10()
```

Rail
----
```{r}
tmp <- data.frame(list(
  rail=style$rail$type,
  id=paste0(style$run, '-', style$rail$id),
  time=style$`Document::updateStyle`))
tmp <- tmp[complete.cases(tmp),]
tmp <- ddply(tmp, .(rail, id), summarize, time=sum(time))
```

Found `r nrow(tmp[tmp$rail != 'unknown',])` RAIL interaction records.
`r round(nrow(style[style$rail$type == 'unknown',]) / nrow(style), 4) * 100`%
of observations were not classified:

* `r nrow(tmp[tmp$rail == 'rail_response',])` response
* `r nrow(tmp[tmp$rail == 'rail_animate',])` animate
* `r nrow(tmp[tmp$rail == 'rail_idle',])` idle
* `r nrow(tmp[tmp$rail == 'rail_load',])` load

Individual observations:

```{r}
ggplot(style, aes(`Document::updateStyle`, color=rail$type)) +
  geom_line(stat="density") + scale_x_log10(breaks=c(1,16,100))
```

Aggregated by RAIL iteraction record:

```{r}
ggplot(tmp[tmp$rail == 'rail_load' | tmp$rail == 'rail_response',], aes(time, color=rail)) +
  geom_line(stat="density") + scale_x_log10(breaks=c(1,16,100))
```

Callees
-------
```{r}
tmp <- reshape2::melt(style$children)
colnames(tmp) <- c('child', 'duration')
childTime <- round(sum(na.omit(tmp$duration)) / sum(na.omit(style$`Document::updateStyle`)), 4) * 100
```

`r childTime`% of thread time spent in traced children.

```{r}
ggplot(tmp, aes(duration)) +
  geom_density(aes(y=..count.., fill=child), position="stack", size=0) + scale_x_log10()
```

Callers
-------
```{r}
v8 <- style[unlist(lapply(style$ancestors, function(x)'V8.Execute' %in% x)), ]
v8_stack <- nrow(v8) / nrow(style)
v8_time <- sum(na.omit(v8$`Document::updateStyle`)) / sum(na.omit(style$`Document::updateStyle`))
```

There were `r length(unique(paste0(style$ancestors)))` unique trace stacks.
`r round(v8_stack, 4) * 100`% of stacks and
`r round(v8_time, 4) * 100`% of thread time
involves `V8.Execute`.

```{r}
for (i in 1:5) {
  style[,paste0("ancestor", i)] <- unlist(lapply(style$ancestors, function(x) {
    v <- unlist(x)[i]
    return(ifelse(is.null(v), NA, v))
  }))
}

treemap::treemap(style, index=c("ancestor1", "ancestor2", "ancestor3", "ancestor4", "ancestor5"), vSize=c("Document::updateStyle"))
```

Style Sharing
-------------

```{r}
style$stylesShared <- (style$counters$sharedStyleFound
                       - style$counters$sharedStyleRejectedByParent
                       - style$counters$sharedStyleRejectedByUncommonAttributeRules)

styleWithCounters <- style[!is.na(style$counters$matchedPropertyCacheHit),]
```

Style sharing rate: `r round(sum(styleWithCounters$stylesShared) / sum(styleWithCounters$resolverAccessCount), 4) * 100`%

```{r}
ggplot(style, aes(stylesShared/resolverAccessCount)) +
  geom_line(stat="density") + scale_y_log10()

ggplot(style[style$resolverAccessCount < 2000, ], aes(`Document::updateStyle`, resolverAccessCount, color=stylesShared/resolverAccessCount, size=stylesShared/resolverAccessCount)) + geom_point(alpha=0.5) + scale_y_log10() + theme(legend.position="top") + guides(color=FALSE)

ggplot(style[style$resolverAccessCount < 2000, ], aes(`Document::updateStyle`/resolverAccessCount, stylesShared/resolverAccessCount)) + geom_point(alpha=0.5) + scale_x_log10()
```

Matched properties cache
------------------------

Non-inherited hit rate: `r round(sum(styleWithCounters$counters$matchedPropertyCacheHit) / sum(styleWithCounters$resolverAccessCount - styleWithCounters$stylesShared), 4) * 100`%

Inherited hit rate: `r round(sum(styleWithCounters$counters$matchedPropertyCacheInheritedHit) / sum(styleWithCounters$resolverAccessCount - styleWithCounters$stylesShared), 4) * 100`%

```{r}

style$stylesMatched <- style$counters$matchedPropertyCacheHit

ggplot(style, aes(stylesMatched/(resolverAccessCount - stylesShared))) +
  geom_line(stat="density")

ggplot(style[style$resolverAccessCount < 2000, ], aes(`Document::updateStyle`, resolverAccessCount, color=stylesMatched/(resolverAccessCount-stylesShared), size=stylesMatched/(resolverAccessCount-stylesShared))) + geom_point(alpha=0.5) + scale_y_log10() + theme(legend.position="top") + guides(color=FALSE)

ggplot(style[style$resolverAccessCount < 2000, ], aes(`Document::updateStyle`/resolverAccessCount, stylesMatched/(resolverAccessCount-stylesShared)))+ geom_point(alpha=0.5) + scale_x_log10()
```

Rules matched / rejected
------------------------
```{r}
styleWithCounters$counters$rules <- (styleWithCounters$counters$rulesMatched
                           + styleWithCounters$counters$rulesRejected
                           + styleWithCounters$counters$rulesFastRejected)
```

Of the rules considered:

* `r round(sum(styleWithCounters$counters$rulesMatched) / sum(styleWithCounters$counters$rules), 4) * 100`% matched
* `r round(sum(styleWithCounters$counters$rulesFastRejected) / sum(styleWithCounters$counters$rules), 4) * 100`% were rejected by the bloom filter
* `r round(sum(styleWithCounters$counters$rulesRejected) / sum(styleWithCounters$counters$rules), 4) * 100`% were rejected by evaluation

```{r}
ggplot(style, aes(counters$rulesMatched / (resolverAccessCount - stylesShared))) +
  geom_line(stat="density")

ggplot(style, aes((counters$rulesRejected + counters$rulesFastRejected) / (resolverAccessCount - stylesShared))) +
  geom_line(stat="density")

ggplot(style, aes(counters$rulesFastRejected / (counters$rulesRejected + counters$rulesFastRejected))) +
  geom_line(stat="density")
```

Styles un/changed
-----------------
```{r}
styleWithUnchanged <- style[!is.na(style$counters$stylesUnchanged), ]
```

Warning: This section isn't entirely accurate yet.

Based on `r nrow(styleWithUnchanged)` `Document::updateStyle` observations.

`r round(sum(styleWithUnchanged$counters$stylesUnchanged) / sum(styleWithUnchanged$resolverAccessCount), 4) * 100`% of styles produced were identical to the previous state.

```{r}
ggplot(styleWithUnchanged, aes(counters$stylesUnchanged / resolverAccessCount)) +
  geom_line(stat="density") + xlim(0, 1)
```